Radiance - A Web Application Environment

### 2016-12-18 els2017-radiance/paper.tex
Tweaked highlighting
Some improvements thanks to @tehrengruber

%% FIXME:
% Tweak minted colours
% Clarify different perspective (admin vs dev)

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usemintedstyle{autumn}
\bibliographystyle{abbrv}

@@

\numberofauthors{1}
\author{
\alignauthor
Nicolas Hafner\\
       \affaddr{ETH Zürich}\\
       \affaddr{Nürenbergstr. 17B}\\
       \affaddr{8037 Zürich, Switzerland}\\
       \email{shinmera@tymoon.eu}
}
\date{15 November 2016}

@@

\section{Introduction}
Writing a website or web application is usually not a very complex or complicated process; doing so involves performing very similar tasks every time. This trend lead to the rise of web frameworks-- collections of tools and libraries to take care of the most common of aspects for the developer. \\

@@

The URL on which the request arrives is transformed into an internal representation by mapping routes. This internal representation, called a ``URI'', is composed of a list of subdomains, an optional port, and a path string. The other information contained in a URL is not necessary for routing or dispatching. Then the request is dispatched to the first handler that matches the URI. It can decide what to do with it, which is usually to render some kind of template. In order to ensure that links and references within the emitted HTML can actually be resolved, the template system must use URIs that are then translated by reversal routes to produce a URL. The completed HTML document is then sent back as a response to the request. \\

>>>>

%% FIXME:
% Clarify different perspective (admin vs dev)
% Clarify "on any server setup"
% Show examples for shitty frameworks
% Focus more on new perspective rather than making the impossible possible or whatever the fuck I was thinking at the tim
% Give more code samples
% In the request cycle image, replace Application with Application/Handler
% Virual subdomains because localhost no subdomains, what fucking idiots specified this shit
% Note about lack of configuration for dev vs prod in conclusion

\documentclass{sig-alternate}
\usepackage[english]{babel}
\usepackage{float}
\usepackage{graphicx}
\usepackage{xcolor}
\usepackage{minted}
\usemintedstyle[html]{borland}
\usemintedstyle[common-lisp]{pastie}
\bibliographystyle{abbrv}

@@

\numberofauthors{1}
\author{
\alignauthor
Nicolas Hafner\\
       \affaddr{ETH Zürich}\\
       \affaddr{Rämistrasse 101}\\
       \affaddr{8092 Zürich, Switzerland}\\
       \email{shinmera@tymoon.eu}
}
\date{15 November 2016}

@@

\section{Introduction}
Most tasks involved in writing a website or web application are not very complex or complicated; they usually involve performing very similar tasks every time. This trend lead to the rise of web frameworks-- collections of tools and libraries to take care of the most common of aspects for the developer. \\

@@

The URL on which the request arrives is transformed into an internal representation by so-called ``mapping routes''. This internal representation, called a ``URI'', is composed of a list of subdomains, an optional port, and a path string. The other information contained in a URL is not necessary for routing or dispatching. Then the request is dispatched to the first handler that matches the URI. It can decide what to do with it, which is usually to render some kind of template. In order to ensure that links and references within the emitted HTML can actually be resolved, the template system must use URIs that are then translated by so-called ``reversal routes'' to produce a URL. The completed HTML document is then sent back as a response to the request. \\
